\documentclass[a4paper,10pt]{article}

% ==============================================================================
% --- COMPACT (LOSSLESS-STYLE) FORMATTING KNOBS ---
% ============================================================================

% 1. Margins: mildly tightened to help one-page fit
\usepackage[a4paper, top=0.25in, bottom=0.2in, left=0.52in, right=0.52in]{geometry}

% 2. List spacing: slightly tighter
\usepackage{enumitem}
\setlist[itemize]{
  leftmargin=1.35em,
  rightmargin=0pt,
  itemsep=0.7pt,
  topsep=0.6pt,
  parsep=0pt,
  partopsep=0pt,
  label=\textbullet
}

% 3. Section title spacing: compact and readable
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{3pt}{1pt}

% 4. General paragraph spacing: mildly tightened
\setlength{\parindent}{1pt}
\setlength{\parskip}{0.4pt}

% 5. Table row and line spacing: near-default with slight tightening
\renewcommand{\arraystretch}{1.0}
\linespread{1.0}

% ==============================================================================
% --- END OF KNOBS ---
% ============================================================================

\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\pagenumbering{gobble}

\begin{document}

\begin{center}
    {\LARGE \textbf{Mohamed Tarek Ismail}}\\[4pt]
    New Cairo, Egypt \quad | \quad
    \href{mailto:mohamedtarekisamil@gmail.com}{mohamedtarekisamil@gmail.com} \quad | \quad
    +20 1507024101\quad | \quad
    \href{https://linkedin.com/in/mtis}{LinkedIn} \quad | \quad
    \href{https://mohamedtareq24.github.io/}{GitHub}
    \quad Military Service: Completed
\end{center}

%--------------------------------------
\section*{Education}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
    \textbf{M.Sc. in Computers and Systems Engineering (CSE)} & 2025 -- Now\\
    \textit{Ain Shams University}
\end{tabular*}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
    \textbf{B.Sc. in Electronics and Communication Engineering (ECE)} & 2019 -- 2024 \\
    \textit{Ain Shams University}
\end{tabular*}
\vspace{1mm}
\textbf{Graduation Project: ASIC Physical  Implementation of PULPino SoC} \hfill Sponsored by \textbf{ICpedia}
\begin{itemize}
    \item Executed the PnR flow using Design Compiler, ICC2, StarRC, and PrimeTime for the PULPino RISC-V SoC.
    \item Developed TCL scripts for Floor Planning , CTS , PnR , Parasitic extraction \& Timing Sign off
    \item Resolved MCMM timing violations via timing ECOs achieving 667 MHz timing closure.
\end{itemize}

%--------------------------------------
\section*{Experience}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\textbf{Verilog \& FPGA Instructor} -- \textit{National Telecommunications Institute} & Aug 2025 -- Nov 2025 \\
\end{tabular*}
\begin{itemize}
  \item Delivered lectures and labs on RTL design and FPGA implementation of HW/SW systems.
\end{itemize}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\textbf{FPGA/ASIC Full-Time Intern} -- \textit{Valeo} & Oct 2024 -- Dec 2024 \\
\end{tabular*}
\begin{itemize}
  \item Developed \& Integrated SV behavioral reference model for SCALA 3 LiDAR verification.
  \item Automated FPGA state extraction scripts to initialize reference models aiding debugging.
\end{itemize}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\textbf{Design \& Verification Trainee} -- \textit{ICpedia} & Aug 2024 -- Sep 2024 \\
\end{tabular*}
\begin{itemize}
    \item SERDES Channel Equalization Techniques.
    \item CDC \& RDC Techniques
    \item UVM \& RAL
\end{itemize}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\textbf{FPGA/Firmware Intern} -- \textit{SiliconArts} & Dec 2023 -- Jun 2024 \\
\end{tabular*}
\begin{itemize}
  \item Executed hardware/software integration of a \textbf{Vortex RISC-V GPU} on an FPGA platform.
  \item Integrated the AXI XDMA PCIe subsystem for host-to-FPGA data transfer and incorporated XDMA software drivers into the Vortex testing code.
\end{itemize}

\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\textbf{Digital Design Summer Trainee} -- \textit{Analog Devices} & Aug 2023 -- Sep 2023 \\
\end{tabular*}
\begin{itemize}
  \item Designed the RTL for a \textbf{3x3 matrix inversion sub-block} targeting both FPGA and ASIC flows,achieving timing closure at 300 MHz.
\end{itemize}

%--------------------------------------
\section*{Projects}
\textbf{Tape-Out of a Quantized CNN ECG Classifier on SkyWater 130\,nm}\hfill American University in Cairo
\begin{itemize}
\item Implemented a tiny ECG arrhythmia classifier using HLS4ML.\hfill
\href{https://github.com/mohamedtareq24/QPulse-Tiny-ECG-classifier-ASIC}{\textbf{GitHub}}
    \item Developed a \textbf{pyuvm} verification environment for end-to-end verification of the ECG inference pipeline.
    \item Executed a host-driven FPGA prototyping flow to validate the ASIC RTL
    \item Performed full ASIC PnR using \textbf{LibreLane}, meeting placement and routing closure under the 1\,mm$^2$ floorplan.
\end{itemize}

\textbf  {Design , Verification \& FPGA implementation of a MIPI D-PHY layer}\hfill
\begin{itemize}
  \item Design of a MIPI D-PHY PHY layer in SystemVerilog with clock and data lane CIL supporting HS, LP, and ULPS operating modes per the MIPI D-PHY specification.
  \item Verified the design using a UVM testbench with a PPI UVC and SVA assertions verifying D-PHY timing specs.
  \item Implemented the HS analog front-end on Xilinx FPGA using Xilinx IO primitives, synthesized and mapped via Vivado.
\end{itemize}
\textbf{SERDES Elastic Buffer Design \& Verification}\hfill  \href{https://github.com/mohamedtareq24/Elastic-Buffer-Design-UVM-Verification}{\textbf{{GitHub}}}
\begin{itemize}
    \item Designed the RTL for an Elastic Buffer using SystemVerilog running on 250 MHz.
    \item Developed a UVM environment with Write and Read agents for asynchronous data domains, alongside an APB UVC that supports UVM RAL.
    \item Developed a clock agent to model Spread Spectrum Clocking (SSC)
    \item Verified data integrity and SKP Ordered Set handling across independent clock domains using Scoreboard \& SVA
    \item Developed functional coverage models to ensure compliance with USB 3 Gen1 specifications.
\end{itemize}

\textbf{Multichannel Router Verification (UVM \& RAL)}
\begin{itemize}
    \item Built a UVM Testbench incorporating multiple Rx/Tx packet, host bus for configuration clocking \& reset UVCs.
    \item Implemented constrained random stimulus generation and hardware register verification via RAL.
    \item Developed a scoreboard to verify end-to-end packet routing and data integrity.
    \item Developed Virtual sequences and system-level tests.
\end{itemize}

\textbf{AXI4 FIR Filter on Zynq MPSoC}\hfill \href{https://github.com/mohamedtareq24/DSP_Custom_AXI_IPs/blob/main/docs/FIR/Readme.md} {\textbf{GitHub}}
\begin{itemize}
    \item Designed a custom AXI4-Stream FIR IP using Verilog.
    \item Integrated the hardware IP with the Zynq Processing System.
    \item Verified data transactions and system functionality using Embedded C routines.
\end{itemize}

%--------------------------------------
\enlargethispage{7\baselineskip}
\vspace{1pt}
\section*{Certifications}
\vspace{1pt}
\begin{itemize}[leftmargin=1.1em,itemsep=0pt,topsep=0pt,partopsep=0pt]
  \item \textbf{SystemVerilog Accelerated Verification with UVM} \hfill \textit{Cadence}
  \item \textbf{Essential SystemVerilog for UVM} \hfill \textit{Cadence}
  \item \textbf{SystemVerilog Assertions} \hfill \textit{Cadence}
\end{itemize}

\end{document}
